\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\lastupdated{Updated April 2025}
\name{Tsang Cheuk Nam} % Your name
% You can merge both of these into a single line, if you do not have a website.
% \address{\href{mailto:harrytsangcn@gmail.com}{harrytsangcn@gmail.com} \\ \href{https://harrytsangcn.csproject.org/}{harrytsangcn.csproject.org}}  
% \address{\href{https://github.com/h9419}{github.com/h9419} \\ \href{https://linkedin.com/in/cheuk-nam-tsang-2997671b3}{linkedin.com/in/cheuk-nam-tsang-2997671b3}}
\address{\href{mailto:harrytsangcn@gmail.com}{harrytsangcn@gmail.com} \\ \href{https://github.com/h9419}{github.com/h9419}}  
\address{\href{https://linkedin.com/in/cheuk-nam-tsang-2997671b3}{linkedin.com/in/cheuk-nam-tsang-2997671b3}}
\address{+852 6699 4301 \\ Hong Kong SAR, China} 

\begin{document}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages       & CUDA, C++, OpenMP, ADSP Assembly, TypeScript, Python, Scala, C\#, Bash           \\
        Frameworks      & React, Redux-Saga, .NET Framework, Flutter, React Native, Node.js, Platform-IO   \\
        Tools           & Git, Linux, Docker, PyTorch, CuBlas, LaTeX, Regular Expression, Mermaid Diagram \\
        % Hands-on Skills & SMT Soldering, Laser Cutter Maintenance, 3D Printing, Oscilloscope Reading
        \\
    \end{tabular}\\
\end{rSection}
% %----------------------------------------------------------------------------------------
% % Projects
% %----------------------------------------------------------------------------------------
% \begin{rSection}{PROJECTS}
%     \vspace{-1.25em}
%     \item \textbf{ESP Access Point Webserver} {C++, Platform-IO, Javascript, React (2021)} \hfill \href{https://github.com/h9419/ESP_AP_Webserver}{GitHub}
%     \begin{itemize}
%         \itemsep -3pt {}
%         \item Created a template for future ESP32-based projects.
%         \item Implemented an access point with captive portal to web application.
%         \item Configured the toolchain to build and upload React web applications.
%         \item Implemented an example React application that controls GPIO via WebSocket.
%     \end{itemize}
%     \item \textbf{Flutter remote controller for Samsung Smart TVs} {Dart, Flutter (2021)} \hfill \href{https://github.com/h9419/flutter_samsung_remote}{GitHub}
%     \begin{itemize}
%         \itemsep -3pt {}
%         \item Configured Internet permission and Adaptive Icon for Android build.
%         \item Implemented automatic access token caching.
%         \item Implemented wake-on-lan for the Smart TVs.
%         \item Implemented touch-pad and keyboard mapping.
%         \item Implemented hardware volume button capturing.
%     \end{itemize}
%     % \item \textbf{Project 3} {Language 1, Framework 1, Database, Language 2, Framework 2, DevOps Tooling} \hfill \href{www.github.com/GITHUBURL}{GitHub}
%     % \begin{itemize}
%     %     \itemsep -3pt {}
%     %     \item Created a XYZ feature to accomplish ABC.
%     %     \item Retrieved data from XYZ to for ABC.
%     %     \item Implemented XYZ library for ABC.
%     %     \item Utilized XYZ that increased A by B\%.
%     % \end{itemize}
% \end{rSection}

%----------------------------------------------------------------------------------------
%------------------------
% Use this more detailed section if you have Relevant work experience
% keep your resume to 1 page, if you need to remove a project to display relevant experience
% that is okay
% ----------------------------
% \begin{rSection}{EXPERIENCE}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \end{rSection} 

\begin{rSection}{Employment History}
    \vspace{-1.25em}
    \item \textbf{Software Architect} {Time Medical Limited Hong Kong}
    \hfill Nov 2024 - Present\\
    
    \hspace*{1cm}%
    \begin{minipage}{.8\textwidth}%
        Responsibilities in this role included:
        \begin{itemize}
            \item Lead the software R\&D team in exploring and integrating new technologies into existing products to increase value proposition to existing clients.
            \item Lead in a major refactoring effort to modernize development workflows and improve developer productivity.
        \end{itemize}
        
        Achievements in this role included:
        \begin{itemize}
            \item Reduced memory footprint of the computational process in an MRI scan by 40\% and opened the possibility to apply more computationally expensive techniques in the current install base of MRI systems.
            \item Documented previously undefined behavior of legacy software and planned out the road-map to rebuild the software infrastructure and improve developer efficiency.
        \end{itemize}
    \end{minipage}%
    
    \item \textbf{Software Developer} {Time Medical Limited Hong Kong}
    \hfill Jul 2023 - Oct 2024 (1 year 4 months)\\
    
    \hspace*{1cm}%
    \begin{minipage}{.8\textwidth}%
        Responsibilities in this role included:
        \begin{itemize}
            \item Research and implement image processing algorithms and medical imaging sequences for MRI machines in C++ and CUDA.
            \item Validate and improve the accuracy of DSP Assembly code for scientific instruments.
            \item Administrate and maintain a fleet of GPU-enabled virtual machines for internal services.
        \end{itemize}

        Achievements in this role included:
        \begin{itemize}
            \item Identified the source of a long-standing issues with one of the scientific instrument's accuracy, and implemented a novel solution that is backward compatible while reducing the error to the level of measurement uncertainty.
            \item Lead the effort in finding the root cause of intermittent crashes, fixing the and reduced memory footprint of the .NET Framework application for MRI machines.
            \item Created internal quality assurance tools that utilizes image recognition to automatically identify problems and alert responsible parties during development.
            \item Lead in migrating and standardizing documentation formats of standard operating procedure, making it more searchable with updated points of contacts.
        \end{itemize}
    \end{minipage}%
    
    \clearpage

    \item \textbf{Software Engineer} {Lalamove Hong Kong} \hfill Jul 2022 - Jul 2023 (1 year)\\ 
    
    \hspace*{1cm}%
    \begin{minipage}{.8\textwidth}%
        
        Responsibilities in this role included:
        \begin{itemize}
            \item Develop new feature for and maintain the user-facing web application front-end.
            \item Consult with product managers during feature ideation phase to illuminate potential technical issues prior to implementation.
            \item Perform deployment and be on call for any abnormalities that may require swift actions to resolve issues.
            \item Maintain documentation and styling for a set of React components used across multiple web pages
        \end{itemize}
        
        Achievements in this role included:
        \begin{itemize}
            \item Lead the team in refactoring JavaScript to TypeScript to increase type safety and deliver features faster. Finishing 100\% conversion to TypeScript in a quarter million line of code code-base without incurring delay in feature releases.
            \item Reducing daily web application crash rates by over 90\% among users with accessibility features enabled by identifying an issue with string composition in React and fixing it using static analysis to highlight the problematic code patterns.
        \end{itemize}
    \end{minipage}%
    
    \item \textbf{Software Engineer} {TURNED-E! Education Limited} \hfill Dec 2021 - Feb 2022 (3 months contract) \\
    
    \hspace*{1cm}%
    \begin{minipage}{.8\textwidth}%
        
        Responsibilities in this role included:
        \begin{itemize}
            \item Develop software and hardware for embedded systems used in STEM Education for K-12 students.
        \end{itemize}
        
        Achievements in this role included:
        \begin{itemize}
            \item Developed the complete ESP32 firmware and application for a STEM education kit that implements a WebSocket server in C++ to perform real-time data transfer to the web client and present the multi-modal data on the web client.
            \item Implemented a standalone IO interface in FPGA and enabled more verbose debugging of internal states during FPGA HDL development.
        \end{itemize}
    \end{minipage}%
    
    
    \item \textbf{Laboratory Technician} {The Hong Kong University of Science and Technology} \hfill Jan 2019 - Dec 2021 (part-time) \\
    
    \hspace*{1cm}%
    \begin{minipage}{.8\textwidth}%
        
        Responsibilities in this role included:
        \begin{itemize}
            \item Maintain and upkeep the shared makerspace in HKUST.
            \item Educate other students on machines safety and laboratory rules.
            \item Advise for student and provide insight on their student initiated projects.
        \end{itemize}
        
        Achievements in this role included:
        \begin{itemize}
            \item Implemented an in-house student card access solution that authorizes and log student usage of laser cutter machine.
        \end{itemize}
        
    \end{minipage}%
    % % \item \textbf{Software Engineer} {DearFans} \hfill Dec 2020 - Jan 2021 (2 months) \\
    % % Full stack developer to develop the company's website and mobile app from the ground up using React.js and Flutter.
    % \item \textbf{Web Developer} {The Hong Kong University of Science and Technology} \hfill Jun 2020 - Sep 2020 (4 months contract) \\
    % Organizing, renovating and building of the University's engineering education center's websites for internal use.
    % % \item \textbf{Laboratory Technician} {The Hong Kong University of Science and Technology} \hfill Aug 2019 - Sep 2019 (2 months) \\
    % % Managing and maintaining the undergraduate student experiential learning lab in the university.
\end{rSection}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    
    {\bf BEng in Computer Science}, The Hong Kong University of Science and Technology \hfill {2018 - 2022}\\
    Honors: First Class Honor\\
    CGA: 3.595\\
    Major-CGA: 3.728
    % Graduated: 2022
    
    %Minor in Linguistics \smallskip \\
    %Member of Eta Kappa Nu \\
    %Member of Upsilon Pi Epsilon \\
    
    
\end{rSection}

\begin{rSection}{Awards}
    \begin{itemize}
        \item 	HKUST Hackathon 2021 semi-finalist
        \item	HKUST CSE Big Idea Challenge 2022 1\textsuperscript{st} Runner-up.
        \item   HKUST Dean's list 2021-2022 Spring
        \item   HKUST Dean's list 2018-2019 Spring
    \end{itemize}
\end{rSection}



\end{document}